\chapter{Theoretical aspects of application}
In this chapter we will takl about the communication protocol,
describe used algorithms (with an accent on steganography), 
overview various possible communication channels (carriers).
% TODO remove if won't be.
We will also talk briefly about resistance of used algorithms
against additional compression of image with embedded message.
We will end this chapter with a list of ''good practices''
a user should follow to achieve maximum possible security
and undetectability.


\section{Communication protocol}
In this section we will describe how the communication works.

% TODO insert the communication diagram

\section{Used algorithms}
In this section we will describe algorithms that we used in our application
and discuss their suitness for our purpose. 
We have had to find a balance between potential quality of the algorithms 
and the cost of their implementation/incorporation.

% TODO find a better way to say it?
\textit{We'd like to mention that these algorithms are not the product of our work.}

\subsection{Steganographic algorithm: Complementary embedding}
% TODO link to the whole paper

\subsubsection{Description}
% the whole algorithm (with listings?)

\subsubsection{Choosing correct parameters}
% address the original paper

\subsubsection{Maximum safe length of the message}

\subsection{Cryptographic algorithm: AES}
% TODO description and link to more specific paper
% TODO add link to implementation
% TODO add link to the original paper

\subsection{Compression algorithm: GZIP}
% TODO link to original paper or standard


\section{Resistance against additional compression}
% TODO it is bad :)


\section{Communication channels}
In this section we will enlist communication channels that are suitable for our purpose.
% TODO really? :D

\section{How to use the application correctly}
In this section we will describe common mistakes and give some advices on
how to achieve maximum inconspicuousness.

\paragraph{Never use the same image twice}

\paragraph{Never send the same message twice}

\paragraph{Change your keys frequently}

\paragraph{Use small images}
% TODO or rather bigg? vivid? black-white?

\paragraph{Try to write your messages as short as possible}

\paragraph{Generate your keys by app's utilities, not by hand}

% TODO something about key management?
